\documentclass{article}
\usepackage[a4paper, margin=1in, top=15mm]{geometry}
\begin{document}
\begin{flushleft}
\textbf{Siddharth Nohria} \\
Department of Computer Science and Engineering \\
Indian Institute of Technology Kanpur, India \\
\textit{Email: snohria@iitk.ac.in} \\
\end{flushleft}
\hrule
\vspace{0.3 em}
\hrule
\vspace{0.3 em}

\begin{flushleft}
I am a second year B-tech student currently pursuing 4th sem in IIT Kanpur. I am the kind of person who knows how to execute difficult tasks with precision. I pay attention to all the details of a project. I make sure that every task is just right, but is also completed in a timely manner. I enjoy solving problems, troubleshooting issues, and coming up with solutions in a timely manner. I would like to do the research in areas like Machine Learning.
\end{flushleft}

\hrule
\vspace{0.3 em}
\hrule
\vspace{0.3 em}


\begin{flushleft}
\textbf{Education} \\
\vspace{3mm}
\begin{tabular}{ |c|c|c|c| }
 \hline
 Matriculation & 2014 & D.A.V Public school, Amritsar & 10.0/10.0 \\
 \hline
 Intermediate & 2016 & D.A.V Public school, Amritsar & 97.2\% \\
 \hline
 B. Tech & 2020 & Indian Institute of Technology, Kanpur  & 9.2/10.0 \\
 \hline
\end{tabular}
\\
\vspace{7mm}
\textbf{Course Details} \\
\vspace{3mm}
\begin{tabular}{ |c|c|c| }
 \hline
 Semester & Total Credits & Highlights \\
 \hline
 Aug 2016 - Dec 2016 & 53 & ESC - 101 \\
 \hline
 Jan 2017 - May 2017 & 51 & MTH - 102 \\
 \hline
 Aug 2017 - Dec 2017 & 50 & CS - 201 \\
 \hline
 Jan 2018 - May 2018 & 58 & ESO - 207 \\
 \hline
\end{tabular}
\\
\vspace{7mm}
\textbf{Skills} \\
\vspace{3mm}
Computer Science \hspace{11mm} : \hspace{3mm} Operating Systems, Machine Learning \\
Programming Languages \hspace{1mm} : \hspace{3mm} C, C++, Python, Scripting languages(bash, awk) \\
\vspace{7mm}
\textbf{Projects} \\

\begin{enumerate}
  \item \textbf{Joint Seat Allocation 2018} \\
  \begin{itemize}
      \item Rewrote the algorithm for Joint Allocation of seats in IITs, NITs and IIITs, 2018.
      \item Improved the time effeciency of the existing Algorithm
      \item Implemented reservation for females ensuring no male student suffers.
  \end{itemize}
  \item \textbf{Game Theory} \\
  \begin{itemize}
      \item Read about zero-sum games and their implementation.
      \item Wrote the algorithm for tic-tac-toe and Connect4 games using minimax algorithm and alpha beta pruning.
  \end{itemize}
\end{enumerate}
\vspace{7mm}
\textbf{Awards and Achievements} \\
\begin{itemize}
    \item[-] Awarded the \textbf{Academic Excellence Award} with a certificate of merit at IIT Kanpur\hfill 2016-17\\[-0.6 cm]
    \item[-] \textbf{JEE Advance (2016).} Secured \textbf{All India Rank of 229} out of 1.5 lakh qualified students \hfill 2016-17\\[-0.6 cm]
    \item[-] \textbf{JEE Mains.} Secured \textbf{All India Rank of 87} out of 1.5 million students\hfill 2016-17\\ [-0.6 cm]
    \item[-] \textbf{KVPY Fellowship} Fellowship given to about 800 students by IISC Bangalore \hfill 2014-15\\
\end{itemize}
\vspace{7mm}
\textbf{Hobbies} \\
\begin{itemize}
    \item[-]  Sports : Badminton, Table Tennis
    \item[-]  Reading Novels
\end{itemize}

\end{flushleft}
\end{document}
